EEG characterization and classification based on histograms of visual gradients

### 2016-12-20 coverletter.tex
Added ApeBrainStorm changes.

This submitted article encompass the work that we have been doing in a context of a PhD thesis and in the context of the setup of a Brain Computer Interfaces Laboratory at the Computer Engineering Department of the ITBA University in Buenos Aires Argentina.

>>>>

en el contexto de nuestra labor en el bci lab en el departamento bla bla b

This submitted article encompass the work that we have been doing and in the context of the setup of a Brain Computer Interfaces Laboratory at the Computer Engineering Department of the ITBA University in Buenos Aires Argentina.

Son areas de investigacion en las cuales nosotros podemos llegar a contribuir como ingenieros e investigadores a los efectos de brindar nuevos metodos y herramientas que favorezcan la comunicación o el tratamiento de individuos que han sido dañados o afectados por enfermedades neuro degenerativas
